Size-differentiated Export in different Dynamical Regimes in the Ocean

### 2019-06-21 size_differentiated_export.tex
Updates from Overleaf

% FIG4
\begin{figure}[ht]
	\centering
	\includegraphics[width = .6\linewidth]{figures/Fig4_particle_PDF}
	\caption{Number of particles (solid) and biomass (dashed) normalized to the fastest-sinking particle class as a function of sinking velocity $w_s$. Sinking velocity spectrum are shown for three different Junge slope $\xi$: 4 (red), 3 (black), and 2 (blue).}
	\label{fig: sinking_velocity_spectrum}
\end{figure}

>>>>

% FIG4
\begin{figure}[ht]
	\centering
	\includegraphics[width = .49\linewidth]{figures/Fig4b.png}
	\includegraphics[width = .49\linewidth]{figures/Fig4a.png}
	\caption{Relative number of particles (left) and biomass (right) as a function of sinking velocity $w_s$. Sinking velocity spectrum are shown for three different Junge slope $\xi$: 2 (dotted), 3 (solid), and 2 (dashed). Colored squares indicate the sinking velocities of the three particle classes modeled: 0.025 m/day (red), 1 m/day (green), and 5 m/day (blue).}
	\label{fig: sinking_velocity_spectrum}
\end{figure}
